%-------------------------
% Resume in LaTeX
% Author : Zade Ammar
% Based off of: Jake Gutierrez (https://github.com/sb2nov/resume)
% License : MIT
%------------------------

\documentclass[letterpaper,10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

%----------FONT OPTIONS----------
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[default]{sourcesanspro}
% \usepackage{CormorantGaramond}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-0.6in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure PDF is machine-readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{\item\small{{#1 \vspace{-2pt}}}}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small#2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Abdulrahman Awad} \\ \vspace{7pt}
    \small 613-410-8305 $|$ 
    \href{mailto:abdulrahmansawad@gmail.com}{\underline{abdulrahmansawad@gmail.com}} $|$
    \href{https://linkedin.com/in/abdulrahmansawad}{\underline{linkedin.com/in/abdulrahmansawad}} $|$
    \href{https://github.com/AbduAwad}{\underline{github.com/AbduAwad}} \\
\end{center}

%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
  \resumeSubheading
    {Carleton University}{Ottawa, ON}
    {Bachelor of Computer Science Honours, Artificial Intelligence and Machine Learning Stream}{Sep 2022 -- April 2026}
    \resumeItemListStart
      \resumeItem{\textbf{GPA:} 4.00/4.00 (A+)}
      \resumeItem{\textbf{Awards:} Golden Key Society, Entrance Scholarship, 2022 - 2025 Deans’ Honour List.}
    \resumeItemListEnd
\resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Programming Languages:} Python, Ruby on Rails, JavaScript, TypeScript, Java, Go, C, C++, SQL, HTML, CSS. \\
     \textbf{Tools and Frameworks:} Linux, iOS, Bash, PyTorch, TensorFlow, Keras, Scikit-Learn, Pandas, Numpy, React, Node, LangChain. \\
     \textbf{DevOps:} CI/CD, Git, GitHub, Gitlab, Graphite, Docker, GCP, AWS, Unit Testing, Integration Testing, End-to-end Testing. \\
     \textbf{Certifications:} Nokia Certified Network Routing Specialist I.
    }}
 \end{itemize}

%-----------EXPERIENCE-----------
\section{Experience}
\resumeSubHeadingListStart

  \resumeSubheading
    {Shopify}{Sep 2025 -- Dec 2025}
    {Software Engineer Intern}{Ottawa, ON}
\resumeItemListStart
\resumeItem{Built a \textbf{GraphQL API} enabling merchants to reverse scheduled cancellations, retaining an average of \textbf{280+} stores weekly.}
\resumeItem{Integrated \textbf{Apple Pay} and \textbf{Google Pay} in Shopify's merchant checkout via \textbf{Stripe Express Pay Elements}, prototyping and developing the vaulting flow to enable faster checkout and increased conversion.}
\resumeItem{Developed an \textbf{Observe dashboard} tracking \textbf{P90 latency}, API errors, and usage metrics across \textbf{1,000+} daily merchant sessions, reducing incident response time through real-time alerts.}

\resumeItemListEnd

  \resumeSubheading
    {Nokia}{May 2025 -- Aug 2025}
    {Automation Engineer Intern}{Ottawa, ON}
    \resumeItemListStart
      \resumeItem{Automated the release pipeline by building a \textbf{GitLab CI/CD} workflow that tested, packaged, and deployed a Go-based security agent, reducing release time by \textbf{90\%}.}
      \resumeItem{Implemented an intelligent \textbf{auto-complete} feature in \textbf{Golang} for the CLI, decreasing SR Linux configuration time by \textbf{70\%} and preventing operator errors.}
    \resumeItemListEnd

  \resumeSubheading
    {Carleton University}{Sep 2023 -- April 2025}
    {Undergraduate Teaching Assistant for Data Structures and Algorithms}{Ottawa, ON}
    \resumeItemListStart
      \resumeItem{Designed \textbf{automated test suites} measuring runtime and correctness, ensuring accurate grading for \textbf{200+} submissions.}
      \resumeItem{Led coding workshops for \textbf{100+} students, teaching algorithmic design patterns and data-driven problem solving.}
      \resumeItem{Conducted \textbf{50+} code reviews, mentoring students in Python and Java best practices and writing clean, efficient code.}
    \resumeItemListEnd

  \resumeSubheading
    {Nokia}{May 2024 -- Aug 2024}
    {Software Engineer Intern}{Ottawa, ON}
    \resumeItemListStart
      \resumeItem{Developed a Workflow Manager \textbf{VSCode extension} in \textbf{TypeScript} to streamline workflow automation for \textbf{600+} engineers.}
      \resumeItem{Reduced data retrieval latency from \textbf{100 ms → 0.001 ms} via an in-memory caching layer achieving \textbf{O(1)} lookup efficiency.}
      \resumeItem{Integrated Nokia’s \textbf{Network Service Platform APIs} to enhance large-scale developer productivity within VSCode.}
    \resumeItemListEnd

  \resumeSubheading
    {Nokia}{May 2023 -- Aug 2023}
    {Automation Developer Intern}{Ottawa, ON}
    \resumeItemListStart
      \resumeItem{Created a \textbf{Python library} leveraging subprocess to automate command execution and validation on \textbf{Linux}, cutting runtime by \textbf{80\%}.}
      \resumeItem{Built a distributed monitoring solution with \textbf{Collectd} and \textbf{Redis} for real-time telemetry of network performance metrics.}
    \resumeItemListEnd

\resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
\resumeSubHeadingListStart

  \resumeProjectHeading
      {\textbf{Git Merge Conflict Resolver - VSCode Extension} $|$ \emph{HuggingFace, PyTorch, TensorFlow, Keras, Scikit-Learn}}{}
      \resumeItemListStart
        \resumeItem{Developed a Neural-Network-powered VSCode extension using a BiLSTM classifier and fine-tuned transformer to auto-resolve Python merge conflicts with \textbf{95\%} accuracy, replicating real-world Git workflows.}
      \resumeItemListEnd

  \resumeProjectHeading
      {\textbf{Carleton University AI Schedule Generator} $|$ \emph{Python, REST APIs, BeautifulSoup, Pandas}}{}
      \resumeItemListStart
        \resumeItem{Generated \textbf{100+} personalized course schedules using AI-based search heuristics, maintaining \textbf{100\%} compliance with registration constraints and preferences.}
      \resumeItemListEnd

  \resumeProjectHeading
      {\textbf{Neural Network Image Classifier} $|$ \emph{Python, PyTorch, TensorFlow, Pandas, Numpy}}{}
      \resumeItemListStart
        \resumeItem{Trained a hybrid \textbf{CNN + RNN} model for handwritten-digit classification, achieving \textbf{94\%} accuracy on test datasets.}
      \resumeItemListEnd

\resumeSubHeadingListEnd

%-------------------------------------------
\end{document}
